\LARGE \bf Experimental Validation of Reference Spreading for Robotic Manipulation of Unmodeled Objects

### 2022-11-30 PaperPreliminary.tex
a

    A logistical aspect where machines struggle to fully compete with humans is object manipulation. Practical examples of this include order picking or depalletizing. While robots are strong and consistent when manipulating objects, humans are versatile and swift. Robots are held back from faster performance because they must often slow down prior to making contact; establishing contact at a high velocity -- an event referred to as an impact -- could cause damage to the robot or its environment. On the contrary, humans intrinsically exploit impacts in the form of grabbing, bouncing and hitting.

@@

    \textbf{4. Intermediate impact phase controller:}

@@

    The Franka Emika robot \cite{haddadinFrankaEmikaRobot2022} is used for the setup as it is affordable and, more importantly, capable of torque control which is critical for impact-aware manipulation. The robot uses harmonic drives that inherently have poor backdriveability, however, torque control is still possible thanks to the torque sensors.

@@

@@

    \subsection{Base controller}
    For articulated robot arms, it is convenient to control the pose of the end effector in Cartesian space, rather than controlling the joint angles. This can be accomplished with an impedance controller.

@@

    \subsection{Custom end effector}

% Teleoperation
    \section{Trajectory planning with teleoperation}

>>>>

    An example of automation in logistics can be found in depalletizing, where object are removed from a pallet. Three different depalletizing approaches can be found in industry.

    A logistical aspect where machines struggle to fully compete with humans is object manipulation. A practical examples of this is depalletizing. While robots are strong and consistent when manipulating objects, humans are versatile and swift. Robots are held back from faster performance because they must often slow down prior to making contact; establishing contact at a high velocity -- an event referred to as an impact -- could cause damage to the robot or its environment. On the contrary, humans intrinsically exploit impacts in the form of grabbing, bouncing and hitting. (give better explanation of depalletizing: manual and automatic approach)

@@

    \textbf{(4. Intermediate impact phase controller:)}

@@

    The Franka Emika robot \cite{haddadinFrankaEmikaRobot2022} is used for the setup as it is affordable and, more importantly, capable of torque control which is critical for impact-aware manipulation. The robot uses harmonic drives that inherently have poor backdriveability, however, torque control is still possible thanks to the torque sensors. Franka Emika provides robot safety limits, such as maximum joint torques or velocities, that should not be exceeded, as this will trigger the

@@

    (image of robots)

@@

    \section{Soft end effector design}

    \subsection{Base controller}
    For articulated robot arms, it is convenient to control the end effector in Cartesian space, rather than directly controlling the robot's joints. In the case of the 7-DoF Franke Emika robot, this leaves one redundant DoF however. Furthermore, despite the desire to control the end effector Carthesian space,

    This can be accomplished with an impedance controller.

@@
